tstrait: a quantitative trait simulator for ancestral recombination graphs

### 2023-11-07 paper.tex
Fixup bib

\abstract{
\textbf{Summary:}
Ancestral recombination graphs (ARGs) encode the entire ensemble of correlated
genealogical trees arising from recombination in a compact and efficient
structure, and are of fundamental importance in population and statistical
genetics. Recent breakthroughs have made it possible to simulate and
infer ARGs at the population scale, and there is now intense interest
in applying ARG-based methods across a broad range of applications.
Genome-wide association studies (GWAS) are one of the most imporant
application areas, with ARG-based methods already providing substantial
improvements over the state-of-the-art. The ability to efficiently
simulate quantitative traits is critical to developing
and evaluating new GWAS methods, but existing simulators do not scale
to modern datasets and cannot be directly applied to inferred or simulated ARGs.
We present the \texttt{tstrait} package,
an open-source Python library to simulate
quantitative traits on ARGs, and show how this user-friendly software
can be easily applied to vast, population-scale datasets.
\\\textbf{Availability and Implementation:} \texttt{tstrait} is available
for download on the Python Package Index.
Full documentation with examples and workflow
templates is available on \url{https://tskit.dev/tstrait/docs/}, and the
development version is maintained on Github
(\url{https://github.com/tskit-dev/tstrait}).\\ \textbf{Contact:}
\href{daiki.tagami@hertford.ox.ac.uk}{daiki.tagami@hertford.ox.ac.uk}\\
}

%\abstract{Abstracts must be able to stand alone and so cannot contain %citations to
%the paper's references, equations, etc. An abstract must consist of a single
%paragraph and be concise. Because of online formatting, abstracts must appear
%as plain as possible.}
%\keywords{keyword1, Keyword2, Keyword3, Keyword4}

@@

Genome-wide association study (GWAS) tests genetic variants across the entire
genome of individuals to identify genetic variants that are statistically
associated with a specific trait \citep{uffelmann2021}. GWAS has successfully
identified many loci that are associated with various human diseases and traits
\citep{ishigaki2022,locke2015,mahajan2022,mathieson2023,yengo2022}, and GWAS
results have actively been used in human trials and clinical practices
\citep{visscher2017}. In spite of its advantages, population structure and
demographic histories can heavily influence GWAS results \citep{uffelmann2021},
so it would be necessary for researchers to implement these factors when
conducting GWAS.

>>>>

\abstract{
\textbf{Summary:}
Ancestral recombination graphs (ARGs) encode the ensemble of correlated
genealogical trees arising from recombination in a compact and efficient
structure, and are of fundamental importance in population and statistical
genetics. Recent breakthroughs have made it possible to simulate and
infer ARGs at the population scale, and there is now intense interest
in applying ARG-based methods across a broad range of applications.
Genome-wide association studies (GWAS) are one of the most imporant
application areas, with ARG-based methods already providing substantial
improvements over the state-of-the-art. The ability to efficiently
simulate quantitative traits is critical to developing
and evaluating new GWAS methods, but existing simulators do not scale
to modern datasets and cannot be directly applied to ARGs.
We present the \texttt{tstrait} package,
an open-source Python library to simulate
quantitative traits on ARGs, and show how this user-friendly software
can be easily applied to vast, population-scale datasets.
\\\textbf{Availability and Implementation:} \texttt{tstrait} is available
for download on the Python Package Index.
Full documentation with examples and workflow
templates is available on \url{https://tskit.dev/tstrait/docs/}, and the
development version is maintained on Github
(\url{https://github.com/tskit-dev/tstrait}).\\ \textbf{Contact:}
\href{daiki.tagami@hertford.ox.ac.uk}{daiki.tagami@hertford.ox.ac.uk}\\
}

%\abstract{Abstracts must be able to stand alone and so cannot contain %citations to
%the paper's references, equations, etc. An abstract must consist of a single
%paragraph and be concise. Because of online formatting, abstracts must appear
%as plain as possible.}
\keywords{Ancestral Recombination Graph, ARG, GWAS, quantitative traits}

@@

Genome-wide association studies (GWAS)
identify genetic variants that are statistically
associated with a specific trait~\citep{uffelmann2021}.
GWAS has successfully
identified many loci that are associated with various human diseases and
traits~\citep{locke2015,ishigaki2022,mahajan2022,yengo2022,mathieson2023},
and GWAS results are being actively incorporated into clinical
practice~\citep{visscher2017}.
Despite these successes, however, there are fundamental issues with
In spite of its advantages, population structure and
demographic histories can heavily influence GWAS results \citep{uffelmann2021},
so it would be necessary for researchers to implement these factors when
conducting GWAS.
